Hypertension and microbiome

### 2019-10-09 articletwo.Rmd
Decrease core

```{r defining genus core}
pseq.genus.core <- microbiome::transform(pseq.genus, "compositional") %>%
    core(detection = 0.0001, prevalence = 0.01)
```

@@

```{r deseq results table}
results(dds, contrast = c("HYPERTENSION", 0, 1)) %>%
    as.data.frame %>%
    tibble::rownames_to_column("Feature") %>%
    dplyr::mutate(qval = p.adjust(pvalue, method="BH")) %>%
    dplyr::filter(qval < 0.05) %>%
    kable
```

```{r deseq plot}
g.deseq <- results(dds, contrast = c("HYPERTENSION", 0, 1)) %>%
    as.data.frame %>%
    tibble::rownames_to_column("Feature") %>%
    dplyr::mutate(qval = p.adjust(pvalue, method="BH")) %>%
    dplyr::filter(qval < 0.05) %>%
    ggplot(aes(x=Feature, y=log2FoldChange, color=qval)) +
    geom_point(size=1) +
    geom_hline(yintercept = 0, color = "gray") +
    theme(axis.text.x = element_text(angle = -90, hjust = 0, vjust=0.5)) +
    coord_flip() +
    theme_classic()

ggsave(file = "cache/deseq.png", plot=g.deseq, height=10, width=5)
```

@@

>>>>

```{r defining genus core}
pseq.genus.core <- microbiome::transform(pseq.genus, "compositional") %>%
    core(detection = 0.001, prevalence = 0.01)
```

@@

```{r deseq results}
dset.deseq.signf <- results(dds, contrast = c("HYPERTENSION", 0, 1)) %>%
    as.data.frame %>%
    tibble::rownames_to_column("Feature") %>%
    dplyr::mutate(qval = p.adjust(pvalue, method="BH")) %>%
    dplyr::filter(qval < 0.05)

dset.deseq.boxplot <- pseq.genus %>%
    microbiome::transform(., transform = "compositional") %>%
    prune_taxa(pull(dset.deseq.signf, Feature), .) %>%
    psmelt %>%
    mutate(Abundance = sqrt(Abundance))
```

```{r deseq results numerical}
dset.deseq.signf %>% kable
```

```{r deseq plot}
g.deseq <- dset.deseq.signf %>%
    ggplot(aes(x=gsub("g_", "", Feature), y=log2FoldChange, color=qval)) +
    geom_point(size=1) +
    geom_hline(yintercept = 0, color = "gray") +
    theme(axis.text.x = element_text(angle = -90, hjust = 0, vjust=0.5)) +
    coord_flip() +
    xlab("Feature") +
    theme_classic()
ggsave(file = "cache/deseq.png", plot=g.deseq, height=8, width=5)
```

@@

```{r deseq boxplot}
g.boxplot <- dset.deseq.boxplot %>% 
    ggplot(aes(x=HYPERTENSION, y=Abundance, color = OTU)) +
    geom_boxplot(lwd=0.1, outlier.size = 0.1) +
    scale_y_continuous(limits = c(0, 0.5)) +
    scale_x_discrete(labels=c("0" = "Normotensive", "1" = "Hypertensive")) +
    ylab("Sqrt For Relative Abundances") +
    theme_classic() +
    guides(shape = guide_legend(override.aes = list(size = 0.1)),
           color = guide_legend(override.aes = list(size = 0.1))) +
    theme(legend.title = element_text(size = 4), 
          legend.text  = element_text(size = 4),
          legend.key.size = unit(1, "lines"),
          legend.position="bottom")
ggsave(file = "cache/dds-test.png", plot=g.boxplot, height=7, width=6, units = "in", dpi = 300)
```

<img src = "cache/dds-test.png" />
